Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex

However, many of these sites have APIs that provide programmatic access to raw sensor data.  Our approach has been touse such APIs to retrieve a patient's information from all services corresponding to their devices.  In particular, we propose that consolidating such information into a uniform, common taxonomy and description logic, like those provided by SNOMED-CT~\cite{stearns2001snomed} and ICD-10~\cite{world1993icd} for diseases, would enable such diaries to be interpretable and used directly by future clinical medical systems, such as primary care information management systems.

>>>>

However, most of these sites have APIs providing programmatic access to raw sensor data.  Our approach has been to leverage such APIs to retrieve a patient's information from all their devices, consolidating it into a uniform, common taxonomy and description logic, like those provided by SNOMED-CT~\cite{stearns2001snomed} and ICD-10~\cite{world1993icd}.  A uniform representation enables such data to be interpretabled and used directly by future clinical medical systems, such as primary care information management systems.
